\begin{rubric}{P R O F E S S I O N A L ~~ E X P E R I E N C E}

  \entry*[July 2011 - Today]

  \textbf{IT analyst / Quality manager / Internship supervisor at
    \textit{High Performance Computing - Simulation Acceleration}.} Active
  member of the R\&D team, maintaining and improving a \emph{multi-platform}
  software of building thermal simulation written in \emph{C++}, intensively
  using the \emph{Qt} framework. The 30-employees company was growing fast, and
  I could grind my expertise and experience in several professional fields:

  \begin{itemize}

  \item Architectural improvement of the software's publication process: I
    performed code audit and lead major refactorings. I also was the initiator
    of huge improvements at high-level scale on the project technical
    management;

  \item Quality manager: establishment of Key Performance Indicators (static
    code analysis with \emph{CppCheck}, \emph{PMD}), tests automatisation with
    \emph{Qt} and \emph{Python} scripts, unit tests with the \emph{QtTest}
    library, quality improvements on several processes (release, debug, OEMs
    management...);

  \item Customer tailor-made developments and on-site interventions for
    assitance;

  \item Debug manager: I was in charge of the bugs fixing process using
    \emph{Mantis} which consisted in priorisation, assignation, follow-up;

  \item Internship supervisor: business and technical referent about
    development, project management, quality values, communication within the
    company, career perspectives;

  \end{itemize}

  \entry*[Apr. 2008 - Mar. 2011]%

  \textbf{IT analyst at \textit{Strator SAS}.} Active implication at every
  level for the development of a set of software meant to improve selling
  experience for tobacco shops / newspapers shops. Project with a big strategic
  target (upgrade of 100\% of the 10,000 Strator's customers). Thus, volumetric
  was and still is an important constraint on the project. It is composed of 3
  local teams and 2 offshore, costs around 9M\euro{} and has been started 16
  months ago.

  \begin{itemize}
  \item Business specifications and UML conception using \emph{Enterprise
    Architect}. Business rules had to be assimilated and understood very
    quickly due to the short development delay.

  \item Work and team organization followed the AGILE method \emph{Scrum},
    sometimes assuming the role of \emph{Scrum Master}. Thus, I could perfectly
    well \emph{train other people}.

  \item Development of the client-side in \emph{C\#} on \emph{Visual Studio
    2008} with a GUI implemented in \emph{WPF}. Many \emph{design patterns}
    were used in order to make the code simple and yet scalable in spite of the
    client's \emph{great complexity}~;

  \item Development of the server-side in \emph{Java} on \emph{Eclipse}, using
    database \emph{HSQL} for the tests and \emph{Postgres} for the
    production. Use of \emph{Spring} and \emph{Hibernate} to enhance code
    modularity.

  \item Installation and management of the \emph{continuous integration
    environment}~: \emph{automatized compilation} of projects both under
    Windows and Linux, \emph{unitary and non-regression tests} daily passed,
    \emph{automatized code review} for C\# and Java, \emph{installation and
      administration} of team-oriented software like \emph{Subversion},
    \emph{Confluence} wiki or \emph{Jira} bug report.

  \end{itemize}

\end{rubric}
